ECCCos from the Black Box:\\ Faithful Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2023-09-25 paper/body.tex
mostly done

@@

To assess and benchmark the performance of our proposed generator against the state of the art, we generate multiple counterfactuals for different models and datasets. In particular, we compare \textit{ECCCo} and its variants to the following counterfactual generators that were introduced above: firstly; \textit{Schut}, which works under the premise of minimizing predictive uncertainty; secondly, \textit{REVISE}, which is state-of-the-art with respect to plausibility; and, finally, \textit{Wachter}, which serves as our baseline.

@@

We perform benchmarks on eight different datasets from different domains. From the credit and finance domain we include three tabular datasets: Give Me Some Credit (\textit{GMSC})~\citep{kaggle2011give}, \textit{German Credit} and \textit{California Housing} (REFRENCES). All of these are commonly used in the related literature~\citep{karimi2020survey,altmeyer2023endogenous,pawelczyk2021carla}. Following~\citet{schut2021generating} we also include two image datasets: \textit{MNIST}~\citep{lecun1998mnist} and \textit{Fashion MNIST}~\citep{xiao2017fashion}. These are small image datasets but they allow us to easily visually gauge how plausible counteractuals are. (EXPLAIN WHY NO LARGER?) Finally, we also benchmark our generators on multiple synthetic datasets. Detailed descriptions and results for all datasets can be found in the appendix (POINTER).

In the following we will focus on the most relevant results highlighted in Tables~\ref{tab:results-tabular} and~\ref{tab:results-vision}.

@@

@@

Our key finding with respect to Research Question~\ref{rq:faithfulness} is as follows:

\begin{quote}
  We find strong empirical evidence that \textit{ECCCo} consistently achieves state-of-the-art faithfulness, as it was designed to do (Research Question~\ref{rq:faithfulness}).
\end{quote}

With respect to balance the objectives of faithfulness and plausibility (Research Question~\ref{rq:plausibility}) we find the following:

\begin{quote}
  The empirical evidence presented here suggests that \textit{ECCCo} consistently achieves near state-of-the-art plausibility without sacrificing faithfulness (Research Question~\ref{rq:plausibility}). 
\end{quote}

\textit{ECCCo} achieves this result primarily by leveraging the model's generative property.

>>>>

Concerning feature autoencoding ($f: \mathcal{Z} \mapsto \mathcal{X}$), \textit{ECCCo} does not rely on latent space search to achieve its primary objective of faithfulness. By default, we choose $f(\cdot)$ to be the identity function as in \textit{Wachter}. This is generally also enough to achieve plausibility, provided the model has learned plausible explanations for the data. In some cases, plausibility can be improved further by mapping counterfactuals to a lower-dimensional latent space. In the following, we refer to this approach as \textit{ECCCo+}: that is, \textit{ECCCo} plus dimensionality reduction.

@@

To assess and benchmark the performance of our proposed generator against the state of the art, we generate multiple counterfactuals for different models and datasets. In particular, we compare \textit{ECCCo} and its variants to the following counterfactual generators that were introduced above: firstly; \textit{Schut}, which works under the premise of minimizing predictive uncertainty; secondly, \textit{REVISE}, which is state-of-the-art (SOTA) with respect to plausibility; and, finally, \textit{Wachter}, which serves as our baseline. In the case of \textit{ECCCo+}, we use Principal Component Analysis for dimensionality reduction: the traversed latent space $\mathcal{Z}$ is spanned by the first $n_z$ principal components where we choose $n_z$ to be equal to the latent dimension of the VAE that is used by \textit{REVISE}.

@@

We perform benchmarks on eight datasets from different domains. From the credit and finance domain we include three tabular datasets: Give Me Some Credit (\textit{GMSC})~\citep{kaggle2011give}, \textit{German Credit} and \textit{California Housing} (REFRENCES). All of these are commonly used in the related literature~\citep{karimi2020survey,altmeyer2023endogenous,pawelczyk2021carla}. Following~\citet{schut2021generating} we also include two image datasets: \textit{MNIST}~\citep{lecun1998mnist} and \textit{Fashion MNIST}~\citep{xiao2017fashion}. These are small image datasets but they allow us to easily visually gauge how plausible counterfactuals are. (EXPLAIN WHY NO LARGER?) Finally, we also benchmark our generators on multiple synthetic datasets. Detailed descriptions and results for all datasets can be found in the appendix (POINTER).

In the following, we will focus on the most relevant results highlighted in Tables~\ref{tab:results-tabular} and~\ref{tab:results-vision}. The tables show sample averages along with standard deviations for our key evaluation metrics for the \textit{California Housing} and \textit{GMSC} datasets (Table~\ref{tab:results-tabular}) and the \textit{MNIST} dataset (Table~\ref{tab:results-vision}). For each metric, the best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). For the tabular datasets, we use the default Euclidian distance to measure unfaithfulness and implausibility as defined in Equations~\ref{eq:faith} and~\ref{eq:impl}, respectively. For the vision datasets, we instead rely on measuring the structural dissimilarity between images~\citep{wang2003multiscale}.

@@

Overall, we find strong empirical evidence suggesting that \textit{ECCCo} consistently achieves state-of-the-art faithfulness. Across all models and datasets highlighted here, all variations of \textit{ECCCo} consistently outperform all other generators with respect to faithfulness, in many cases substantially. This pattern is mostly robust across all other benchmark datasets (Tables~\ref{tab:results-linearly-separable} to~\ref{tab:results-fashion-mnist}).

In particular, we note that the best results are generally obtained when using the full \textit{ECCCo} objective (Equation~\ref{eq:eccco}). In other words, constraining both energy and predictive uncertainty typically yields the most faithful counterfactuals. We expected the former to play a more significant role in this context and that is typically what we find across all datasets. For example, the results for \textit{GMSC} in Table~\ref{tab:results-tabular} indicate that faithfulness can be improved substantially by relying solely on the energy constraint (\textit{ECCCo (no CP)}). In some cases though, as for the \textit{California Housing} dataset, \textit{ECCCo (no EBM)} actually outperforms \textit{ECCCo (no CP)}. This indicates that predictive uncertainty minimization plays an important role in achieving faithfulness.

We also generally find that the highest degree of faithfulness is obtained when the counterfactual search is performed directly in the feature space $\mathcal{X}$. While \textit{ECCCo+} typically attains high levels of faithfulness compared to most other generators, it is consistently outperformed by \textit{ECCCo}. The case is even stronger for \textit{REVISE}, which performs worst out of all generators for faithfulness on the \textit{GMSC} dataset and better only than \textit{Wachter} on \textit{California Housing}.

These findings are consistent with the notion that surrogate models may inhibit faithfulness. Even though dimensionality reduction through PCA in the case of \textit{ECCCo+} can be considered a relatively mild form of intervention, the first $n_z$ principal components fail to capture some of the variation in the data, that the underlying model itself may be sensitive to. This notion is illustrated nicely in Figure~\ref{fig:mnist-bmk}, where the counterfactual produced by \textit{ECCCo} is somewhat noisier and grainier than the one produced by \textit{ECCCo+}.

In conclusion, we recommend in light of the findings here to use the full \textit{ECCCo} search objective whenever model faithfulness is a key priority.

% Sample UUID of factual: UUID("1ceb06f0-5949-11ee-0e9c-dd49ccfec8c3")

@@

Overall, we find strong empirical evidence suggesting that \textit{ECCCo} can achieve near state-of-the-art plausibility without sacrificing faithfulness. Figure~\ref{fig:mnist-bmk} shows one such example taken from the \textit{MNIST} benchmark. In this case, the objective was to turn the factual three (far left) into a five. The underlying model is a LeNet-5 convolutional neural network. The different images show the counterfactuals produced by the generators, of which all but the one produced by \textit{Schut} are valid. Both variations of \textit{ECCCo} produce plausible counterfactuals.

Looking at the benchmark results presented in Tables~\ref{tab:results-tabular} and~\ref{tab:results-vision} we firstly note that although \textit{REVISE} generally performs best, \textit{ECCCo} and in particular \textit{ECCCo+} often approach SOTA performance. Zooming in on the details we observe that \textit{ECCCo} and its variations do particularly well, whenever the underlying model has been explicitly trained to learn plausible representations of the data. For both tabular datasets in Table~\ref{tab:results-tabular}, \textit{ECCCo} improves plausibility substantially compared to the baseline. This broad pattern is mostly consistent for all other datasets, although there are notable exceptions for which \textit{ECCCo} takes the lead on both plausibility and faithfulness (see for example Tables~\ref{tab:results-moons} and~\ref{tab:results-german-credit}).

While we maintain that generally speaking plausibility should hinge on the quality of the model, our results also indicate that it is possible to trade off some degree of faithfulness for plausibility if needed: \textit{ECCCo+} generally outperforms other variants of \textit{ECCCo} in this context at the small cost of slightly reduced faithfulness. For the vision datasets especially, we find that  \textit{ECCCo+} is consistently second only to \textit{REVISE} for all models and regularly substantially better than the baseline. Looking at the \textit{California Housing} data, latent space search markedly improves plausibility without sacrificing faithfulness: for the \textit{JEM} Ensemble, \textit{ECCCo+} performs substantially better than the baseline and only marginally worse than \textit{REVISE}. Importantly, \textit{ECCCo+} does not attain plausibility at all costs: for the MLP, plausibility is still very low but this seems to faithfully represent what the model has learned.

We conclude that \textit{ECCCo} offers us a way to balance the objectives of faithfulness and plausibility. \textit{ECCCo+} can be used to tilt the scale in favour of plausibility if needed.

### 2023-09-25 paper/tables.Rmd
mostly done

@@

@@

```{r}
# Choices:
measures <- c(
  "unfaithfulness",
  "implausibility"
)
measure_names <- c(
  "Unfaithfulness ↓",
  "Implausibility ↓"
)
# Order:
chosen_data <- c(
  "Linearly Separable",
  "GMSC",
  "MNIST",
)
chosen_model <- c(
  "MLP",
  "JEM",
  "LeNet-5"
)

@@

# Logic:
tab_i <- tab_i[variable %in% measures]
tab_i <- tab_i[dataname %in% chosen_data]
tab_i <- tab_i[model %in% chosen_model]
tab_i[,dataname:=factor(dataname,levels=chosen_data)]
tab_i <- dcast(tab_i, model + generator ~ dataname + variable)
col_names <- c(
  "Model",
  "Generator",
  rep(measure_names,length(chosen_data))
)
caption <-  "Results for datasets from different domains: sample averages +/- one standard deviation across counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-main} \\newline"
file_name <- "paper/contents/table-main.tex"
sub_header <- rep(length(measures), length(chosen_data))
names(sub_header) <- chosen_data
header <- c(
  " " = 2, sub_header
)
line_sep <- c(rep("",length(measures)-1),"\\addlinespace")
algin_cols <- c(rep('l',2),rep('c',ncol(tab_i)-2))
kbl(
  tab_i, caption = caption, 
  align = algin_cols, col.names=col_names, booktabs = T, escape=F, 
  format="latex", linesep = line_sep 
) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_paper(full_width = T) %>%
  add_header_above(header) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  save_kable(file_name)
```

```{r}
# Choices:
measures <- c(
  "distance_from_energy_l2",
  "distance_from_targets_l2"
)
measure_names <- c(
  "Unfaithfulness ↓",
  "Implausibility ↓"
)
chosen_source <- "tabular"
# Order:
chosen_data <- c(
  "GMSC",
  "California Housing",
  "German Credit"
)
chosen_model <- "MLP"

@@

# Logic:
tab_i <- tab_i[variable %in% measures]
tab_i <- tab_i[source == chosen_source]
tab_i <- tab_i[dataname %in% chosen_data]
tab_i <- tab_i[model == chosen_model]
tab_i[,dataname:=factor(dataname,levels=chosen_data)]
tab_i <- dcast(tab_i, model + generator ~ dataname + variable)
col_names <- c(
  "Model",
  "Generator",
  rep(measure_names,length(chosen_data))
)
caption <- sprintf(
  "Results for %s datasets: sample averages +/- one standard deviation across counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-%s} \\newline",
  chosen_source,
  chosen_source
)
file_name <- sprintf(
  "paper/contents/table-%s.tex",
  chosen_source
)
sub_header <- rep(length(measures), length(chosen_data))
names(sub_header) <- chosen_data
header <- c(
  " " = 2, sub_header
)
line_sep <- c(rep("",length(measures)-1),"\\addlinespace")
algin_cols <- c(rep('l',2),rep('c',ncol(tab_i)-2))
kbl(
  tab_i, caption = caption, 
  align = algin_cols, col.names=col_names, booktabs = T, escape=F, 
  format="latex", linesep = line_sep 
) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_paper(full_width = T) %>%
  add_header_above(header) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  save_kable(file_name)
```

```{r}
# Choices:
# Choices:
measures <- c(
  "distance_from_energy_l2",
  "distance_from_targets_l2"
)
measure_names <- c(
  "Unfaithfulness ↓",
  "Implausibility ↓"
)
chosen_source <- "synthetic"
chosen_data <- c(
  "Linearly Separable",
  "Moons",
  "Circles"
)
tab_i <- tab

# Logic:
tab_i <- tab_i[variable %in% measures]
tab_i <- tab_i[source == chosen_source]
tab_i <- tab_i[dataname %in% chosen_data]
tab_i[,dataname:=factor(dataname,levels=chosen_data)]
tab_i <- dcast(tab_i, model + generator ~ dataname + variable)
col_names <- c(
  "Model",
  "Generator",
  rep(measure_names,length(chosen_data))
)
caption <- sprintf(
  "Results for %s datasets: sample averages +/- one standard deviation across counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-%s} \\newline",
  chosen_source,
  chosen_source
)
file_name <- sprintf(
  "paper/contents/table-%s.tex",
  chosen_source
)
sub_header <- rep(length(measures), length(chosen_data))
names(sub_header) <- chosen_data
header <- c(
  " " = 2, sub_header
)
line_sep <- c(rep("",length(measures)-1),"\\addlinespace")
algin_cols <- c(rep('l',2),rep('c',ncol(tab_i)-2))
kbl(
  tab_i, caption = caption, 
  align = algin_cols, col.names=col_names, booktabs = T, escape=F, 
  format="latex", linesep = line_sep 
) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_paper(full_width = T) %>%
  add_header_above(header) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  save_kable(file_name)
```

```{r}
# Choices:
measures <- c(
  "distance_from_energy_l2",
  "distance_from_targets_l2"
)
measure_names <- c(
  "Unfaithfulness ↓",
  "Implausibility ↓"
)
chosen_source <- "vision"
# Order:
chosen_data <- c(
  "MNIST",
  "Fashion MNIST",
)
chosen_model <- "LeNet-5"

# Logic:
tab_i <- tab_i[variable %in% measures]
tab_i <- tab_i[source == chosen_source]
tab_i <- tab_i[dataname %in% chosen_data]
tab_i <- tab_i[model == chosen_model]
tab_i[,dataname:=factor(dataname,levels=chosen_data)]
tab_i <- dcast(tab_i, model + generator ~ dataname + variable)
col_names <- c(
  "Model",
  "Generator",
  rep(measure_names,length(chosen_data))
)
caption <- sprintf(
  "Results for %s datasets: sample averages +/- one standard deviation across counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-%s} \\newline",
  chosen_source,
  chosen_source
)
file_name <- sprintf(
  "paper/contents/table-%s.tex",
  chosen_source
)
sub_header <- rep(length(measures), length(chosen_data))
names(sub_header) <- chosen_data
header <- c(
  " " = 2, sub_header
)
line_sep <- c(rep("",length(measures)-1),"\\addlinespace")
algin_cols <- c(rep('l',2),rep('c',ncol(tab_i)-2))
kbl(
  tab_i, caption = caption, 
  align = algin_cols, col.names=col_names, booktabs = T, escape=F, 
  format="latex", linesep = line_sep 
) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_paper(full_width = T) %>%
  add_header_above(header) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  save_kable(file_name)
```

## Full table

```{r}
tab_full <- dcast(tab, dataname + model + generator ~ variable)
col_names <- c(
  "Model",
  "Data",
  "Generator",
  "Cost ↓", 
  "Unfaithfulness ↓", 
  "Implausibility ↓", 
  "Redundancy ↑",
  "Uncertainty ↓",
  "Validity ↑"
)
algin_cols <- c(rep('l',3),rep('c',ncol(tab_full)-3))
kbl(
  tab_full, caption = "All results for all datasets: sample averages +/- one standard deviation over all counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-full} \\newline", 
  align = "c", col.names=col_names, booktabs = T, escape=F, 
  format="latex"
) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_paper(full_width = F) %>%
  collapse_rows(columns = 1:3, latex_hline = "custom", valign = "top", custom_latex_hline = 1:2) %>%
  save_kable("paper/contents/table_all.tex")
```

@@

```{r}
tab_full <- dcast(tab_valid, dataname + model + generator ~ variable)
col_names <- c(
  "Model",
  "Data",
  "Generator",
  "Cost ↓", 
  "Unfaithfulness ↓", 
  "Implausibility ↓", 
  "Redundancy ↑",
  "Uncertainty ↓",
  "Validity ↑"
)
algin_cols <- c(rep('l',3),rep('c',ncol(tab_full)-3))
kbl(
  tab_full, caption = "All results for all datasets: sample averages +/- one standard deviation over all valid counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-full-valid} \\newline", 
  align = "c", col.names=col_names, booktabs = T, escape=F, 
  format="latex"
) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_paper(full_width = F) %>%
  collapse_rows(columns = 1:3, latex_hline = "custom", valign = "top", custom_latex_hline = 1:2) %>%
  save_kable("paper/contents/table_all_valid.tex")
```

>>>>

```{r}
generators <- unique(dt$generator)[sapply(unique(dt$generator), function(x) {!grepl("L1",x)})]
tab <- dt[
    generator %in% generators,
    .(
      value=sprintf("%1.2f ± %1.2f", mean(value), sd(value)),
      val = mean(value),
      std = sd(value)
    ),
    .(dataname, generator, model, variable, source)
]

@@

```{r}
generators <- unique(dt$generator)[sapply(unique(dt$generator), function(x) {!grepl("L1",x)})]
tab_valid <- dt_valid[
    generator %in% generators,
    .(
      value=sprintf("%1.2f ± %1.2f", mean(value), sd(value)),
      val = mean(value),
      std = sd(value)
    ),
    .(dataname, generator, model, variable, source)
]

@@

```{r}
# Choices:
measures <- c(
  "unfaithfulness",
  "implausibility",
  "set_size_penalty"
)
measure_names <- c(
  "Unfaithfulness ↓",
  "Implausibility ↓",
  "Uncertainty ↓"
)
chosen_source <- "tabular"
# Order:
chosen_data <- c(
  "California Housing",
  "GMSC"
)
chosen_model <- c(
  "MLP",
  "JEM Ensemble"
)

@@

# Logic:
tab_i <- tab_i[variable %in% measures]
tab_i[,variable:=factor(variable, levels=measures)]
tab_i <- tab_i[dataname %in% chosen_data]
tab_i <- tab_i[model %in% chosen_model]
tab_i[,model:=factor(model,levels=chosen_model)]
tab_i[,dataname:=factor(dataname,levels=chosen_data)]
tab_i <- dcast(tab_i, model + generator ~ dataname + variable)
col_names <- c(
  "Model",
  "Generator",
  rep(measure_names,length(chosen_data))
)
caption <- sprintf(
  "Results for %s datasets: sample averages +/- one standard deviation across counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-%s} \\newline",
  chosen_source,
  chosen_source
)
file_name <- sprintf(
  "paper/contents/table-%s.tex",
  chosen_source
)
sub_header <- rep(length(measures), length(chosen_data))
names(sub_header) <- chosen_data
header <- c(
  " " = 2, sub_header
)
line_sep <- c(rep("",length(measures)-1),"\\addlinespace")
algin_cols <- c(rep('l',2),rep('c',ncol(tab_i)-2))
kbl(
  tab_i, caption = caption, 
  align = algin_cols, col.names=col_names, booktabs = T, escape=F, 
  format="latex", linesep = line_sep, table.env="table*"
) %>%
  kable_styling(
    latex_options = c("scale_down")
  ) %>%
  kable_paper(full_width = F) %>%
  add_header_above(header) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  save_kable(file_name)
```

```{r}
# Choices:
measures <- c(
  "unfaithfulness",
  "implausibility"
)
measure_names <- c(
  "Unfaithfulness ↓",
  "Implausibility ↓"
)
chosen_source <- "vision"
# Order:
chosen_data <- c(
  "MNIST"
)
chosen_model <- c(
  "MLP",
  "LeNet-5"
)

@@

# Logic:
tab_i <- tab_i[variable %in% measures]
tab_i[,variable:=factor(variable, levels=measures)]
tab_i <- tab_i[dataname %in% chosen_data]
tab_i <- tab_i[model %in% chosen_model]
tab_i[,model:=factor(model,levels=chosen_model)]
tab_i[,dataname:=factor(dataname,levels=chosen_data)]
tab_i <- dcast(tab_i, model + generator ~ dataname + variable)
col_names <- c(
  "Model",
  "Generator",
  rep(measure_names,length(chosen_data))
)
caption <- sprintf(
  "Results for %s dataset. Formatting details are the same as in Table~\\ref{tab:results-tabular}. \\label{tab:results-%s} \\newline",
  chosen_source,
  chosen_source
)
file_name <- sprintf(
  "paper/contents/table-%s.tex",
  chosen_source
)
sub_header <- rep(length(measures), length(chosen_data))
names(sub_header) <- chosen_data
header <- c(
  " " = 2, sub_header
)
line_sep <- c(rep("",length(measures)-1),"\\addlinespace")
algin_cols <- c(rep('l',2),rep('c',ncol(tab_i)-2))
kbl(
  tab_i, caption = caption, 
  align = algin_cols, col.names=col_names, booktabs = T, escape=F, 
  format="latex", linesep = line_sep 
) %>%
  kable_styling(
    latex_options = c("scale_down")
  ) %>%
  kable_paper(full_width = F) %>%
  add_header_above(header) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  save_kable(file_name)
```

## Full tables

# Remove redundant columns:
tab[,val:=NULL]
tab[,std:=NULL]
tab[,top_val:=NULL]
tab[,two_std_wachter:=NULL]
tab[,one_std_wachter:=NULL]

# Measures:
measures <- c(
  "unfaithfulness",
  "implausibility",
  "set_size_penalty",
  "distance",
  "redundancy",
  "validity"
)
measure_names <- c(
  "Unfaithfulness ↓",
  "Implausibility ↓",
  "Uncertainty ↓",
  "Cost ↓",
  "Redundancy ↑",
  "Validity ↑"
)
tab <- tab[variable %in% measures]
tab[,variable:=factor(variable, levels=measures)]
```

# Remove redundant columns:
tab_valid[,val:=NULL]
tab_valid[,std:=NULL]
tab_valid[,top_val:=NULL]
tab_valid[,two_std_wachter:=NULL]
tab_valid[,one_std_wachter:=NULL]

# Measures:
measures <- c(
  "unfaithfulness",
  "implausibility",
  "set_size_penalty",
  "distance",
  "redundancy",
  "validity"
)
measure_names <- c(
  "Unfaithfulness ↓",
  "Implausibility ↓",
  "Uncertainty ↓",
  "Cost ↓",
  "Redundancy ↑",
  "Validity ↑"
)
tab_valid <- tab_valid[variable %in% measures]
tab_valid[,variable:=factor(variable, levels=measures)]
```

### Tables (all)

```{r}
for (name in unique(tab$dataname)) {
  data_indicator <- gsub(" ", "-", tolower(unique(name)))
  # Choices:
  tab_full <- dcast(tab[dataname==name], model + generator ~ variable)
  col_names <- c(
    "Model",
    "Generator",
    measure_names
  )
  algin_cols <- c(rep('l',3),rep('c',ncol(tab_full)-3))
  file_name <- sprintf(
    "paper/contents/table-%s.tex", 
    data_indicator
  )
  cap <- sprintf(
    "All results for %s dataset: sample averages +/- one standard deviation over all counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-%s} \\newline",
    name,
    data_indicator
  )
  kbl(
    tab_full, caption = cap, 
    align = "c", col.names=col_names, booktabs = T, escape=F, 
    format="latex"
  ) %>%
    kable_styling(latex_options = c("scale_down")) %>%
    kable_paper(full_width = F) %>%
    collapse_rows(columns = 1:2, latex_hline = "custom", valign = "top") %>%
    save_kable(file_name)
}

```

@@

```{r}
for (name in unique(tab_valid$dataname)) {
  data_indicator <- gsub(" ", "-", tolower(unique(name)))
  # Choices:
  tab_full <- dcast(tab_valid[dataname==name], model + generator ~ variable)
  col_names <- c(
    "Model",
    "Generator",
    measure_names
  )
  algin_cols <- c(rep('l',3),rep('c',ncol(tab_full)-3))
  file_name <- sprintf(
    "paper/contents/table-%s-valid.tex", 
    data_indicator
  )
  cap <- sprintf(
    "All results for %s dataset: sample averages +/- one standard deviation over all valid counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-%s} \\newline",
    name,
    data_indicator
  )
  kbl(
    tab_full, caption = cap, 
    align = "c", col.names=col_names, booktabs = T, escape=F, 
    format="latex"
  ) %>%
    kable_styling(latex_options = c("scale_down")) %>%
    kable_paper(full_width = F) %>%
    collapse_rows(columns = 1:2, latex_hline = "custom", valign = "top") %>%
    save_kable(file_name)
}
```
